\documentclass{article}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\usepackage{a4wide}
\usepackage{float}
\usepackage{listings}

\begin{document}
\title{Report --- Juniour Honours Project Submission 2}
\author{Hafeez Abdul-Rehaman, Johannes Weck, Josh Lee, Calum Duff, Tom Harley}
\date{\today}

\maketitle

\section{Aims for submission 2}
From our first submission we now had a working server that allowed a user using our own mock user interface to log in and access data based on their level of authorisation. After our first submission we had a meeting to set out goals for ourselves that would act as requirements for the second submission 
\begin{description}
  \item[Define Specific Protocol] Now that we had a working server, we next wanted to define specific protocol in order to demo our progress using work from the HCI groups.
  \item[Manage Filetype Conversions] A main part of this submission was creating a file converter for all the required file types that would be needed. 
  \item[Testing] As our code was getting more complicated we wanted to make sure that extensive testing was implemented to create a more secure and consistent system.
\end{description}

\section{Continued use of Scrum}
In general the size and the time taken of each individual task was a lot smaller when comparing them to the last submission. We found using scrum extremely helped in managing this to clearly set out tasks and outline what everyone was doing. 
\subsection{Scrum board}
We again went with using a board system to set up and allocate tasks. This gave a clear visual representation of what we wanted to achieve. With everyone now being in the same location it also made it a lot easier for everyone to set up and manage ongoing tasks. 
\subsection{Sprints}
Now being familiar with the scrum process we decided to reduce the length of the sprints. This was also based on the fact that tasks were smaller and that the sprint assessment process needed to be undertaken more often to make sure we were on the right track with our progress as a team.
\subsection{Meetings}
As we were attempting to do shorter sprints we held more regular meet ups to discuss progress and make design decisions as a team. 
The minutes for formal meetings are available in Appendix \ref{app:meet}.


\section{File Conversions}
\subsubsection{.scn File Converter}
\subsubsection{.czi File Converter}
\subsubsection{.xslx File Converter}


\section{Protocols}
\subsection{Implementing end points}

\section{Authorisation}
\subsection{Connecting Authentication to Middleware}


\section{Testing}
\subsection{Error Handling}
\subsection{Content Checking}


\section{Looking Ahead}

\appendix
\section{Meeting minutes}  \label{app:meet}
\begin{lstlisting} 

Group Project Meeting 1 post submission
Date: 12/02/18 
Topics: 
Reassigning scrum roles 
Creating next set of tasks 
Task allocation 

Outcomes:
* Scrum: 
    * scrum master - Hafeez 
    * project owner - Calum 

*Tasks:
    * Implementing endpoints
    * Implementing file conversions 
    * Improving test coverage 
    * Writing tests for untested sections 
    * Connecting all middleware 
    * Decide on how to deal with errors and connecting 
    * Organising file-system 
    * Creating a Linter to maintain a consistent file structure 

\end{lstlisting}

\end{document}

