\section{Conclusion}
As a group, we are very pleased with the process and outcome of this group project. Our final product consists of substantial contributions from all our team members. It was tested and integrated with the systems produced by ML and HCI groups, completes all of the tasks initially identified and the development relied heavily on our use of scrum. 

For the final deadline we successfully combined all parts of the system into one final server, completing any remaining tasks which included file management, file conversion and testing. Our system was integrated both with our assigned ML and HCI groups, as well as with other groups, thus ensuring the compatibility of our contribution to the whole pathology system. 

\subsection{Future Development}
The submitted project has potential for future improvements, especially regarding system security and file-conversion. 

One substantial flaw of our system is that we rely on the security of all the node-modules including postgres as well as their inter-compatibility. Comprehensive vulnerability scanning as well as penetration testing of our system would be required to ensure security of patients' confidential data. Research into security standards required by law would be necessary.

Similarly, it might prove useful to encrypt data on the server-side as well as combine the ML server and the BE server into one software package, thus reducing the number of components involved.

Also, image file conversion could be explored further, as conversion of *TODO* into png is not yet supported

