\section{File Conversion}
One of the most key pieces of functionality for the backend groups is the facilitation of the agnosticity of
original file formats to the end user. No matter the original upload format, backend groups should all be
capable of returning files in standard file formats.
These specific ``standards'' were not hard-defined by the specification, however as part of our whole year
protocol, it was decided that \emph{JSON} would be used for file meta-information, as well as the
main structure of all responses from a backend server. \emph{PNG} was decided upon as the standard file format
for all images, since it is very widely supported and has other favourable properties we would like to
take advantage of.

\subsection{Dealing with Images}
The nature of the file formats that we were expected to abstract over however turned out to be significantly
more challenging than was initially perceived. The file formats of `Leica' and `Zeiss' are widely used in the
medical field (the department we are providing this service for), however almost nowhere else. Upon looking
into this more closely, it was found that the Zeiss file format is very proprietary and licensed.

This means that in order to even gain access to simply read the documentation you must fill in your details
and make an application for the documentation~\cite{zeissLicence}. Part of the agreement for this documentation is that you are
not allowed to share it with anyone else; you are allowed to write software to \emph{deconstruct} them; you
are strictly \emph{not} allowed to write any software to construct them.

The documentation gives a description of the various ``segments'' of binary that can appear in the file, and
attempts to assist you in the method to read them. Given the large nature of the file size of a Zeiss, it makes
sense for them to be designed to be `streamable', which they are --- allowing you to read smaller chunks at a
time rather than loading the whole object into memory simultaneously.

After reading the specification in great detail, it was clear that it was extremely specialised and has
the potential to nest a variety of other file types within itself, as well as have many fields missing
--- as they are optional --- making it quite complex to interpret. In addition to this, the major difficulty
came from the fact that the base file is a proprietary binary file, which also contains things such as 128bit
unsigned integers. This fact, coupled with the substantial file sizes made the choice for languages to deal
with them limited to a systems programming language. Since I had most experience in `C99', then this seemed
the only realistic possibility.

\subsubsection{Extraction of Zeiss Within `C'}
One major consideration was that --- due to the sheer file size of many of these images --- we would need
to store them on the local \file{/cs/scratch} drive of the lab machines: they are simply too
large to store either on our host servers statically, let alone when working on extracting and expanding the
thousands of smaller files within them.

With this in mind, and closely comparing the
`C' code against the rough documentation licensed to me, the structures possible within a Zeiss file were
slowly built up.

Methods were written to print out the contents of various structures as progress was made, in
order to ensure that the offsets for file streaming were continually at the correct locations and the data we
were parsing out of the file was as expected. To this effect, testing of the extraction was run continually
in the standard `C' approach of a couple lines at a time before re-compilation, along with using flags such as
`\verb|--pedantic|' in order to try to catch as many errors as possible. Occasionally \verb|valgrind| was also
run on this extraction code, since significant chunks of memory are allocated and freed during the
extraction process. \verb|valgrind| reports that there are no memory leaks at all --- even
on the larger 12Gb \file{.czi} files.

\subsubsection{Converting Extracted Files}
Once the files/metadata/attachments had been successfully extracted from the target file, multiple issues were
discovered.
\begin{itemize}
	\item The container format for the image segments was in \emph{JPEG-XR}. This is another proprietary
		file format, which does not appear to be supported by anything at all, other than Microsoft's own software.
		There is also extremely limited library support, especially for non-Windows platforms.
		Fortunately, a C++-written \file{.jxr} decoder was found, and could
		be compiled on the destination machine. Enough of the executable is able to be compiled before any problems
		occur, and this decoder can be copied into the relative path for our own C source.
	\item The library for decoding JXR's is only
		capable of conversion to \emph{BMP} or \emph{TIFF}, which is not our desired format. Therefore an additional step of
		converting the `JXR' to `TIFF', and then to `PNG' using the `imagemagick' command line tools like \verb|convert|
		became necessary.
		This is an annoying overhead, which is unfortunately unavoidable.
	\item By simply extracting every image tile found within the JXR tile, we found that
		there were also tiles found at non 1:1 zoom levels, which was wasteful to deal with, since we will be building
		a custom image pyramid anyway. This issue was mitigated by adding some logic to only extract the tile to disk if
		it was determined to have a 1:1 scaling and thus be on the base layer.
	\item In a similar fashion to the previous issue, it also became apparent that there were many tiles in the
		base layer which were of non-standard sizes, with some having tiny slivers as they came to edges etc.
		The only solution to make these tiles appear on a nice grid of $n^2$ sizes, was to iterate over the fragmented
		canvas and stitch together the portions we want.
\end{itemize}

In order to complete the conversion side of things, it seemed appropriate to move away from C programming, and
even away from the scripts that were being using to control the C, to something like \emph{Python}.
The thought process behind this decision is the fact that Python supports multithreading --- which for something
as parallel as multiple image conversions seemed extremely advantageous. The code to do this section is fairly
small, but absolutely crucial to the overall pipeline of Zeiss format support.

\subsubsection{Stitching Base Tiles}
Once we finally had all of the base tiles in a 1:1 scale and a format that was easier to deal with, the first task
was to figure out how to build up our own grid across the mismatch of sizes of existing base tiles.\\
The tile dimensions decided on were 1024:1024. The reason for this, is that it is large enough to contain a
reasonable amount of information, without being so large that our server could provide or clients could load in
a timely manner.

In order to do this stitching process, a decision was required as to the package to manage the image operations.
After a vast amount of searching and comparisons, the selection was made for \emph{Sharp}~\cite{sharp}. The reason for
this, was that it appeared to be the single library which was capable of all of the different kinds of image
processing jobs we expected to be doing. Another key reason is the fact that it is known in advance that a very
large number of images will need to be processed here, so performance is critical. Sharp appears to perform
very significantly better than its competitors~\cite{sharpPerformance}. Finally, it has typing
support to work with our environment.

With this set, high level logic was written to check various image bounds for related base tiles to a specific
region request. Regions were then selected out, sorted by x and y offsets, then relevant chunks chopped out of
them and stitched together into a coherent region of our selected size.

\subsubsection{Building Up Hierarchy of Zoom Levels}
These finalised base layer tiles are written to disk in an output directory and details about their creation
are recorded in a new data structure which will map out the pyramid style hierarchy of the tiles.
A small example of these final titles are shown on the cover page of our Report for interest as they are
legitimate generations in a format we would like.

Now that the base layer exists, gaining the rest of the tile zoom levels, should be fairly simple --- by moving
up to the next power of two (2048) and collecting 4 images together then scaling this back down to 1024 pixels.
This process can be repeated for each level of zoom we would like to raise to. This will massively speed up
the process of searching through base tiles and stitching many together if we pre-process all of the intermediate
layers. Since most HCI groups are using OpenSeaDragon (which requests things in scales of powers
of two~\cite{openseadragon}), our approach should be a very fast performer with the trade off of larger up-front pre-processing time.\\
Indexing into this pyramid will be extremely fast with each request too, as they will be separated by `C' value, which is
one of the image's layering options, then by zoom level, then you are straight into the 2d plane.

\subsection{Leica \& Other Formats}
As Zeiss is such a difficult and mammoth file format almost all of my time was spent dealing with purely this.
However having looked quickly into Leica, there appears to be
With Leica files, once more research was done into their format, it was found that they are actually identical
to BigTiffs, with the only difference being a meta value which is optional in tif is mandatory in Lecia.

With this discovered, and with our chosen image processing library `sharp' on hand, which can natively convert Tiff to
`.dzi' which is the standard that OpenSeaDragon seems to prefer, then if a file was a Lecia it became as trivial to convert
as other image formats such as JPEG etc.

\subsection{Non image formats (\file{.csv} etc.)}
As for non image formats such as \file{.csv}, it has been decided that the backend should only be responsible of hosting these
files, since there is no way that a backend server could possibly predict what the file should be processed into.
Additionally, there are also many cases where an end-user may wish to deliberately store something in a format
which a backend server checking legitimacy of the file would complain about incorrectly.

Another of the client desired file formats support was Excel (\file{.xlsx}). This was fairly easy to complete too.
We loaded a library that was capable of parsing the binary and transforming it into an object which is easier to work with.
This object can then be converted to csv for each sheet in the workbook and various files written and recorded to describe
how this is lain out.

\subsection{Final Results of conversion}
With the end of Deliverable 3, we carried out some integration testing.
Unfortunately we came across a significant number of problems with regards the running of the conversion code through no fault of our own.

For example, the max filesize of postman was exceded with even the smallest of CZI files. The host servers have some process creation limitations
and therefore do not allow the conversion side of the code to be run on them, as such any and all conversion needed to take place on the
scratch drive of a local lab machine, which is significantly less powerful, and so all testing took substantial time.

Since we were not able to upload the file directly there needed to be some live editing of our postgres database at run time to full the system
into beleiving that it had a file uploaded as a CZI. Much to our delight however, we did get a sample of this working, and found a sucessful
integration with an HCI group, whereby they were able to load the CZI endpoint and zoom and pan the image by requesting tiles precreated by the backend!

The actual computation required to crunch down a CZI file into something that can be easily read and used by the end user is \emph{massive}. Huge amounts
of testing and raw image computation/buffer manipulation is carried out in order to normalise regions and arrange them in a sensible format.
From what we can tell of other backend groups, noone else even attempted to get image support for these formats, yet I have achieved full support.
(albeit in some confined rules of the system environment required to allow the code to actually run).

We are very proud of this level of support, and only wish we had a longer time to test and optimise it further in serving it.
