\section{Conclusion}
As a group a lot of progress was made for this submission, we were proactive in setting out goals for ourselves and feel we are now well on track to produce an outstanding final hand in. Our continued use of scrum has helped keep workload consistent and effective right through to this submission and we hope to continue in this way. Scrum is essential in our progress as it helps to manage time and organise the team work and so this process will be used for the duration of the project. Having now combined our work with the HCI group we are looking forward to working with teams focused on machine learning to tie together all 3 sections of the application to create the desired system set out by the project owner.

\subsection{Next Tasks}
Viewing the system as a whole, substantial progress has been made in completing each required task whilst also managing time for each task appropriately. Looking further ahead, our next objectives will surround performance enhancing, further testing and finally completing the integration process with the rest of the system. The process for these will include a large amount of analysis on the working server, which include finding delays between certain requests and responses, measuring time taken for converting files and testing for bugs after integration. Another important aspect is the security of the application, and preventing bugs from leading to exploits which can be used for malicious use. This is particularly important within the medical industry as data confidentiality and integrity are apart of practitioners' policy. One method of testing for this task would be penetration testing, using a suite of tools to attack the application, which would determine any vulnerabilities that exist.